---
title: "HistDat"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{histdat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First we need to import the package:
```{r setup}
library(HistDat)
```


Now, let's say that we have seen the number one 10,000 times, the number two 20,000 times etc.

If we turned this into a single vector with the true number of each observation,
we would have a vector of length 60,000! That would use a lot of RAM, and we
don't really need to do that

```{r}
h = HistDat(
  vals = 1:4,
  counts = c(10000, 20000, 20000, 10000)
)
```

Now let's calculate some summary statistics, without using RAM we don't need!
```{r}
mean(h)
min(h)
length(h)
median(h)
```

We actually *can* convert a `hist_dat` object into a 1-D vector, which is 
reasonable if we only have a small number of counts:
```{r}
h = HistDat(
  vals = 1:4,
  counts = c(1, 2, 2, 1)
)
as.vector(h)
```
